Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-01-14 paper/plos.tex
add lots of fixmes from referees Tested everything on bennet.

>>>>

\fixme{
  First referee:
  \begin{enumerate}
  \item Add discussion of ``platform'' --- wrote our own code,
    publically available (cite github?).
  \item Make 3D geometries available? Cite that the publically
    available code can generate them?
  \item Claims differential equations aren't needed.
  \item Claims wild-type movie-ish plot not needed.
  \item Points out problems with Huang 2003:
    \begin{enumerate}
    \item Lacks diffusion on the membrane
    \item Underestimates diffusion in cytoplasm by a factor of 5-6.5.
    \item Uses MinD-ADP -> MinD-ATP that is 3 times lower than
      experimental bound.
    \item (Still debated) No evidence that DE recruits to membrane.
    \item Works in only a limited part of parameters phase space, and
      could not account for important things like
      temperature-independence.
    \end{enumerate}
  \item Height should be bigger to compare with experiment.  0.4-0.6
    microns.  \textcolor{blue}{HIGH PRIORITY!!! to figure this out}

    The 0.25 micron height of the cells used in this study does not
    represent the experimental settings well. The simulations are
    based on the flattened cell shapes reported from the experiments
    by Mannik et al 2009 and 2012. In these experimental studies,
    E. coli were shown to be able to grow in channels as low as 0.6
    micron in hard silicon structures, and no more than 0.4 micron
    (see Mannik 2009). Indeed, 0.25 micron channels were constructed
    with PDMS ceilings, which is a rather flexible polymer allowing
    bacteria to deform it to effectively higher channels. Thus the
    simulations would be more realistic if performed in the range of
    0.4-0.6 micron thickness.

    \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
      then we and you observe it growing in a .25 micron flexible
      channel, it presumably must be able to grow because it deformed
      the channel to larger than .3 microns.}
  \item Starry night in the wild-type cells is a problem.
  \item Better explanation of correlation function (which is
    interesting!).
  \item Shape A is the interesting bit in our main figure.
  \item Would like more analysis of stochastic locations in different
    geometries.  Clusters?  Could add more geometries?
  \item Bold conclusions about flattening.  Talk about both width and
    thickness.  Compare Halatek 2012.  Wants systematically more
    geometries again.
  \item Is doubtful of our correlation plots relative to those of
    Fange and Elf 2006.
  \item Clarify (esp in conclusions) what we mean by flattening and
    irregular shape.  ``breaking the cylindrical symmetry and
    flattening the cells.'' versus ``breaking the mirror plane
    symmetry of the cross-section of a flattned cell.''
  \item[TODO suggestion] Switch to Halatek and Frey
  \item[TODO suggestion] Thoroughly explor shape parameter space
  \item[TODO suggestion] Check robustness of our conclusions with
    respect to changes in (reaction-diffusion?) parameters.
  \item Check order of figures and their references.
  \item Cite biological (non-computational) works e.g. Corbin 2008.
  \end{enumerate}
  Second referee:
  \begin{enumerate}
  \item Nitpicks about language of deterministic model versus
    stochastic model.  (Read carefully)
  \item Explain in greater detail the obviousness (maybe) that the
    deterministic approach doesn't have fluctuations.  RESPOND:
    chaotic systems do deterministically result in fluctuations.
    Explain this somewhere, and discuss triviality of the conclusion
    that deterministic is wrong because it does not exhibit these
    irregularities.
  \item Would like temporal averages over cell-cycle time scales.
  \item More discussion of how flattening leads to spatial
    irregularities.  Compare with large nearly spherical e. coli Shih
    2005.  See also Halatek and Frey 2012 for rotating oscillation
    axis due to destabilization of short modes.  How does this connect
    with our stability analysis?
  \item Should mention more recent revisions of the model.
  \item Fange and Elf do not use the same reaction-diffusion
    equations.
  \item Clarify statement about 1000 proteins and stochastic
    fluctuation.  Reword about a continuum description omitting
    information?
  \item Do not call Huang parameters ``wild type values.''  They are
    fitted parameters.
  \item Add methods section for numerics (deterministic).
  \item Add details of the linear stability analysis.
  \end{enumerate}
}

\fixme{Redo stability analysis with larger thickness, whatever we pick.}
